Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-05 paper_jasa.tex
general cleanup

\green{The dashed line cannot be seen in experiment 2 for small effect, and it is essential to see this at this point. What can you do to make the dashed line visible?} \blue{The dashed line layer is placed on top of all other layers. Still there is trouble to see it. Do you think it will work?}

@@

In practice, $p$-value is not going to be a valid way to compare plots. Rather metrics that can measure how graphical elements from one plot to another are perceived similarly are needed. This is investigated in the paper \cite{waldo}. Here numerical measures of the similarity between plots are proposed to provide quality metrics for lineups.

@@

\noindent It was possible to choose more than one reason. The question begged for ``visible trend'' (2) to be the reasons that observers gave for correctly choosing the actual data plot. Either reasons 1 or 3 would be indicative of Type III error. It is interesting to calculate the proportion of observers who choose the correct plot, but use reasons 1 or 3, relative to reason 2. Figure \ref{fig:choice_reason} examines this. For observers who chose the actual data plot, the proportions for the three reasons are shown. It can be seen that the most common reason was ``most different plot'' (1), followed by clustering visible (3), with ``visible trend'' coming in third. \green{What about other??} \blue{Not many people chose other as we see in Figure \ref{fig:choice_reason}.}

>>>>

@@

In practice, $p$-value is not going to be a valid way to compare plots. Rather metrics that can measure how graphical elements from one plot to another are perceived similarly are needed. This is investigated in \citet{niladri:2012}. Here numerical measures of the similarity between plots are proposed to provide quality metrics for lineups.

@@

\noindent It was possible to choose more than one reason. The question begged for ``visible trend'' (2) to be the reason that observers gave for correctly choosing the actual data plot. Either reasons 1 or 3 would be indicative of Type III error. It is interesting to calculate the proportion of observers who choose the correct plot, but use reasons 1 or 3, relative to reason 2. Figure \ref{fig:choice_reason} examines this. For observers who chose the actual data plot, the proportions for the three reasons are shown. It can be seen that the most common reason was ``most different plot'' (1), followed by clustering visible (3), with ``visible trend'' coming in third. \green{What about other??} \blue{Not many people chose other as we see in Figure \ref{fig:choice_reason}.}
